---
title: "Pinterest Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(ggplot2)
library(grid)
library(gridExtra)
library(lattice)
library(tigerstats)
library(formattable)
library(uaparserjs)
library(reshape2)
library(nlme)
library(likert)
library(ordinal)
options(dplyr.print_max = 1e9)
```

###Initial Setup
Read in the data from the file:
```{r}
dat <- read.csv('pinterest_experiment.csv')
nrow(dat)
```

How many duplicate responses do we have?
```{r}
summary(duplicated(dat["workerId"]))
```

What are the column names?
```{r}
names(dat)
```

###Data Wrangling

Rename the columns:
```{r}
dat <- dat %>% rename(pin.impression = `What.is.your.overall.impression.of.the.pin.`,
                      item.impression = `After.observing.the.pin..what.is.your.overall.impression.of.the.item.shown.in.the.image.above.`,
                      creator.favors = `How.much.do.you.think.the.pin.creator.favors.the.item.shown.in.the.image.above.`,
                      relationship = `How.likely.do.you.think.there.is.a.relationship.between.the.pin.creator.and.the.organization.selling.the.item.`,
                      age = `In.which.year.were.you.born.`,
                      gender = `What.is.your.gender.`,
                      education = `What.is.the.highest.level.of.education.you.have.completed.`,
                      income = `What.is.your.annual.household.income.`,
                      account.pinterest = `Pinterest.Which.of.the.following.social.media.platforms.do.you.have.an.account.on.`,
                      visit.pinterest = `Pinterest.How.often.do.you.visit.each.of.the.following.social.media.platforms.`,
                      post.pinterest = `Pinterest.How.often.do.you.post.content.on.each.of.the.following.social.media.platforms.`)
```

Modify the demographics:
```{r}
dat <- dat %>% mutate(age = 2018 - age)
```

Change the relevant columns to factors:

```{r}
dat <- dat %>% mutate(Condition = factor(Condition), 
                      Pin = factor(Pin), 
                      PinId = factor(PinId))

levels(dat$Pin) <- c("Soap", "Seed", "Shoes", "Blanket", "Bed")
levels(dat$Condition) <- c("Control", "AffTop", "AffBottom", "ExplTop", "ExplBottom")
```


Create a new column indicating the disclosure type:

```{r}
dat <- dat %>% mutate(Disclosure = ifelse(Condition == "ExplTop" | Condition == "ExplBottom", "Expl", ifelse(Condition == "AffTop" | Condition == "AffBottom", "Aff", "Control")))
```

Change the relevant columns to numeric:

```{r}
summary(dat$pin.impression)
dat <- dat %>% mutate(pin.impression = (factor(pin.impression, levels=c("Extremely Negative", "Somewhat Negative", "Neutral", "Somewhat Positive", "Extremely Positive"))))
summary(dat$pin.impression)

dat <- dat %>% mutate(pin.impression_numeric = as.numeric(pin.impression))
summary(dat$pin.impression_numeric)

summary(dat$item.impression)
dat <- dat %>% mutate(item.impression = (factor(item.impression, levels=c("Extremely Negative", "Somewhat Negative", "Neutral", "Somewhat Positive", "Extremely Positive"))))
summary(dat$item.impression)

dat <- dat %>% mutate(item.impression_numeric = as.numeric(item.impression))
summary(dat$item.impression)

summary(dat$creator.favors)
dat <- dat %>% mutate(creator.favors = (factor(creator.favors, levels=c("Does Not Favor At All", "Slightly Favors", "Somewhat Favors", "Moderately Favors", "Strongly Favors"))))
summary(dat$creator.favors)

dat <- dat %>% mutate(creator.favors_numeric = as.numeric(creator.favors))
summary(dat$creator.favors)

summary(dat$relationship)
dat <- dat %>% mutate(relationship = (factor(relationship, levels=c("Extremely Unlikely", "Somewhat Unlikely", "Neutral", "Somewhat Likely", "Extremely Likely"))))
summary(dat$relationship)

dat <- dat %>% mutate(relationship_numeric = as.numeric(relationship))
summary(dat$relationship)
```


###User Demographics

How old were the users?

```{r}
summary(dat$age)
sd(dat$age)
```

How were they distributed by gender?

```{r}
rowPerc(xtabs(~gender, data=dat))
```

How were they distributed by education?

```{r}
rowPerc(xtabs(~education, data=dat))
```

How many users do we have in each condition across the survey?
```{r}
xtabs(~Condition + Pin, data=dat)
```

How many users do we have in each disclosure across the suvrey?
```{r}
xtabs(~Disclosure + Pin, data=dat)
```

How many users vs non-users do we have?
```{r}
rowPerc(xtabs(~account.pinterest, data=dat))
```

How often do users visit Pinterest?
```{r}
rowPerc(xtabs(~visit.pinterest, data=dat))
```

How often do users post on Pinterest?
```{r}
rowPerc(xtabs(~post.pinterest, data=dat))
```

Let's write a simple graphing utility.
```{r}
likert_plot <- function(data, pin_factor, col) {
  filt_data <- data %>% filter(Pin == pin_factor)
  cols <- c(col)
  cols <- setNames(cols, c(pin_factor))
  likert_data <- likert(filt_data %>% select(col) %>% rename_(.dots=cols), grouping=filt_data$Condition)
  return(plot(likert_data, centered=FALSE, legend.position="none"))
}

grid_likert_plot <- function(data, col) {
  p1 <- likert_plot(data, "Soap", col)
  p2 <- likert_plot(data, "Seed", col)
  p3 <- likert_plot(data, "Shoes", col)
  p4 <- likert_plot(data, "Blanket", col)
  p5 <- likert_plot(data, "Bed", col)
  
  return(grid.arrange(p1, p2, p3, p4, p5))
}

likert_plot_combined <- function(data, col) {
  likert_data <- likert(data %>% select(col), grouping=data$Condition)
  return(plot(likert_data, centered=FALSE, legend.position="none"))
}
```

Let's also write a utility that will generate the logit plot.
```{r}
po_plot_helper <- function(data, pin_factor, col) {
  filt_data <- data %>% filter(Pin == pin_factor)
  mat <- as.data.frame.matrix(xtabs(formula(paste0("~Condition + ", col)), filt_data))
  
  new_mat <- matrix(nrow=5, ncol=4)
  
  for(i in 1:4) {
     first_set <- mat[, c(1:i)]
     second_set <- mat[, c((i+1):5)]
     
     if(!is.null(dim(first_set))) {
        first_set <- as.integer(rowSums(first_set))
     }
     
      if(!is.null(dim(second_set))) {
        second_set <- as.integer(rowSums(second_set))
     }
 
     result = log(first_set/second_set)
     
     new_mat[, i] <- result
  }
  
  rownames(new_mat) <- rownames(mat)
  return(ggplot(melt(new_mat), aes(x=Var1, y=value, col=factor(Var2), group=factor(Var2))) + geom_line() + xlab("Condition") + ylab("Logits") + theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position="none") + ggtitle(pin_factor))
} 

po_plot <- function(data, col) {
  p1 <- po_plot_helper(data, "Soap", col)
  p2 <- po_plot_helper(data, "Seed", col)
  p3 <- po_plot_helper(data, "Shoes", col)
  p4 <- po_plot_helper(data, "Blanket", col)
  p5 <- po_plot_helper(data, "Bed", col)
  
  return(grid.arrange(p1, p2, p3, p4, p5))
}
```

###What is your overall impression of the pin?

Let's first examine the distribution of this question across the different pins.

```{r}
xtabs(~Condition + pin.impression, data=dat)
```

Let's visualize the data.

```{r}
grid_likert_plot(dat, "pin.impression")
```

Let's visualize the logits.

```{r}
po_plot(dat, "pin.impression")
```

Next, let's build a ordinal regression model.

```{r, warning=FALSE}
model <- clmm2(pin.impression ~ Condition, random=Pin, data=dat, Hess = TRUE)
summary(model)

exp(coef(model))
exp(confint.default(model))
```


###What is your overall impression of the item?

Let's first examine the distribution of this question across the different pins.

```{r}
xtabs(~Condition + item.impression, data=dat)
```

Let's visualize the data.

```{r}
grid_likert_plot(dat, "item.impression")
```

Let's visualize the logits.

```{r}
po_plot(dat, "item.impression")
```

Next, let's build a ordinal regression model.

```{r, warning=FALSE}
model <- clmm2(item.impression ~ Condition, random=Pin, data=dat, Hess = TRUE)
summary(model)

exp(coef(model))
exp(confint.default(model))
```


###How much do you think the creator favors the item?

Let's first examine the distribution of this question across the different pins.

```{r}
xtabs(~Condition + creator.favors, data=dat)
```

Let's visualize the data.

```{r}
grid_likert_plot(dat, "creator.favors")
likert_plot_combined(dat, "creator.favors")
```

Let's visualize the logits.

```{r}
po_plot(dat, "creator.favors")
```

Next, let's build a ordinal regression model.

```{r, warning=FALSE}
model <- clmm2(creator.favors ~ Condition, random=Pin, data=dat, Hess = TRUE)
summary(model)

exp(coef(model))
exp(confint.default(model))
```

###How likely do you think there is a relationship between the content creator and the merchant?

Let's first examine the distribution of this question across the different pins.

```{r}
xtabs(~Condition + relationship, data=dat)
```

Let's visualize the data.

```{r}
grid_likert_plot(dat, "relationship")
```

Let's visualize the logits.

```{r}
po_plot(dat, "relationship")
```

Next, let's build a ordinal regression model.

```{r, warning=FALSE}
model <- clmm2(relationship ~ Condition, random=Pin, data=dat, Hess = TRUE, link="logistic")
summary(model)

exp(coef(model))
exp(confint.default(model))
```